On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement

### 2024-07-17 manuscript/manuscript-si.tex
si: create separate si.tex for elsevier typesetting

% format hacks
\usepackage{libertine}
\usepackage{libertinust1math}
\usepackage{amsmath}                 % Provides advanced math typesetting and environments
\usepackage{bbold}                   % Provides blackboard bold font for numbers
\usepackage{graphicx}                % Handles the inclusion of graphics files
\usepackage{eurosym}                 % Provides the Euro currency symbol
\usepackage{mathtools}               % Enhances amsmath package, adding new symbols and tools
\usepackage{url}                     % Handles the formatting of URLs
\usepackage{booktabs}                % Improves the quality of tables in LaTeX
\usepackage{epstopdf}                % Automatically converts EPS files to PDF
\usepackage{xfrac}                   % Provides a consistent way to typeset fractions
\usepackage{tabularx}                % Enhances the standard LaTeX tables
\usepackage{bm}                      % Provides access to bold math symbols
\usepackage{subcaption}              % Provides support for subfigures and subtables
\usepackage{longtable}               % Allows the creation of multi-page tables
\usepackage{multirow}                % Enables cells spanning multiple rows in tables
\usepackage{threeparttable}          % Provides additional functionality for tables
\usepackage{pdflscape}               % Allows landscape pages in PDF output
\usepackage[svgnames]{xcolor}    	 % Load xcolor packages
\usepackage[export]{adjustbox}       % Provides tools for resizing and trimming images
\usepackage[version=4]{mhchem}       % Provides typesetting for chemical equations
\usepackage{xurl} 				     % Allows line breaks in URLs
\usepackage[colorlinks]{hyperref}    % Creates hyperlinks in the document
\usepackage[parfill]{parskip}        % Adjusts paragraph spacing
\usepackage[nameinlink,sort&compress,capitalise,noabbrev]{cleveref} % Enhanced cross-referencing
\usepackage[leftcaption,raggedright]{sidecap} % Provides side captions for figures and tables
\usepackage[prependcaption,textsize=footnotesize]{todonotes} % Allows inline and margin notes
\usepackage{siunitx}                 % Provides consistent formatting for units and numbers
\usepackage{csquotes} 				 % For handling inline and display quotations
\usepackage[acronym, automake, nonumberlist]{glossaries-extra}

@@

% acronyms
\makeglossaries

% Proper nouns
\newacronym{eu}{EU}{European Union}
\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
\newacronym{dea}{DEA}{Danish Energy Agency}
\newacronym{jrc}{JRC}{Joint Research Center}
\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}

% Enegy tech concepts
\newacronym{tes}{TES}{Thermal Energy Storage (in form of water tanks)}
\newacronym{chp}{CHP}{Combined Heat and Power plant}
\newacronym{cop}{COP}{Coefficient of Performance}
\newacronym{PV}{PV}{Solar photovoltaics}
\newacronym{ghg}{GHG}{Greenhouse gas}
\newacronym{helmeth}{HELMETH}{Integrated High-Temperature Electrolysis and Methanation for Effective Power to Gas Conversion}
\newacronym{ocgt}{OCGT}{Open Cycle Gas Turbine}
\newacronym{v2g}{V2G}{Vehicle to Grid}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{hvdc}{HVDC}{High Voltage Direct Current}
\newacronym{phs}{PHS}{Pumped Hydro Storage}
\newacronym{dac}{DAC}{Direct Air Capture}
\newacronym{sng}{SNG}{Synthetic Natural Gas}
\newacronym{res}{RES}{Renewable Energy Sources}
\newacronym{cfe}{CFE}{Carbon-Free Electricity}
\newacronym{ldes}{LDES}{Long Duration Energy Storage}
\newacronym{ccs}{CCS}{Carbon Capture and Sequestration}

% Energy economics and finance concepts
\newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
\newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
\newacronym{capex}{CAPEX}{Capital expenditures}
\newacronym{opex}{OPEX}{Operational expenditures}
\newacronym{ppa}{PPA}{Power Purchase Agreement}
\newacronym{ptc}{PTC}{Production Tax Credit}
\newacronym{necp}{NECP}{National Energy and Climate Plan}
\newacronym{ets}{ETS}{Emissions Trading System}
\newacronym{cfd}{CfD}{Contract for Difference}
\newacronym{go}{GO}{Guarantees of Origin}
\newacronym{rec}{REC}{Renewable Energy Certificate}

% Other
\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
\newacronym{ci}{C\&I}{Corporate and Industry (sectors)}
\newacronym{ngo}{NGO}{Non-Governmental Organization}

@@

\begin{frontmatter}

	\title{On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement}

	\author[tubaddress]{Iegor Riepin\fnref{fn1}}
	\ead{iegor.riepin@tu-berlin.de}
	\author[tubaddress]{Tom Brown}
	\ead{t.brown@tu-berlin.de}

	\address[tubaddress]{Department of Digital Transformation in Energy Systems, TU Berlin, Germany}
	\fntext[fn1]{Corresponding author: Iegor Riepin, Technical University of Berlin, Einsteinufer 25, 10587 Berlin, Germany}

\begin{abstract}
% The 5 things a good abstract needs:
% 1. Introduce the topic: what we know
% 2. State the unknown: what we don't know
% 3. Outline the methods: how we answer the questions
% 4. Preview the findings: what we learned
% 5. Tell us what your work teaches us: what we conclude and why this is important
% aim ~200 words | working paper: 205 words | revision: 230 words

A growing number of public and private energy buyers are interested in 24/7 carbon-free energy (CFE) procurement, which means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.
It has the potential to overcome the limitations of established procurement schemes, such as the temporal mismatch between clean electricity supply and buyers' demand that is inherent to \enquote{volumetric} matching.
Yet it is unclear how 24/7 CFE procurement affects the rest of the power system, and whether this effect is consistent across regional contexts and different levels of system cleanness.
We use a mathematical model to systematically examine different designs, optimal procurement strategies, costs, and impacts of the 24/7 CFE matching, both for participating buyers and for regions where voluntary procurement occurs.
We examine mechanisms driving system-level emissions reduction and how they vary across regions and over time.
Our results indicate that clean energy procurement commitments have consistent beneficial effects on participants and the electricity system.
Utilizing an hourly matching strategy, energy buyers can eliminate all carbon emissions linked to their electricity consumption, while also reducing system-level emissions by up to 572~kgCO$_2$/a per MWh of participating load.
Even as grids become cleaner over time, the hourly matching strategy contributes significantly to system-level emissions reduction.
In addition, voluntary commitments to 24/7 CFE have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.

\end{abstract}

	\begin{keyword}
		24/7 carbon-free electricity,
		Clean electricity procurement,
		Energy modelling,
		Renewable energy
	\end{keyword}

	% \begin{graphicalabstract}
	% \end{graphicalabstract}

\end{frontmatter}

% \tableofcontents

\section{Introduction}
\label{sec:intro}

% 1. **Opening & Introduce the global momentum towards renewable energy adoption.**

Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe.
The European Union (\gls{eu}) has committed to achieving net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}.
National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have CO$_2$ emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.

% 2. **Evolution, approaches and challenges of voluntary clean energy procurement**

Many public and private energy buyers have joined this effort by purchasing clean energy to demonstrate their sustainability credentials.
The established certification schemes for voluntary clean energy procurement are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (\gls{rec}s) in the United States.
A common feature of these schemes is that renewable energy credits are \enquote{unbundled} from megawatt-hours of energy and can be traded numerous times on specialized markets before being retired.
The owner gets to claim environmental benefits when \enquote{retiring} (i.e. using) the certificate.
The unbundled renewable energy credits, however, have been criticized for not ensuring a physical match between renewable energy generation and consumption \cite{spglobal-recs, bock-icelandGOproblem, re100report-2020}, and for absence of evidence that such schemes drive build-out of additional renewable energy capacity \cite{bjorn-RECSnatcom-2022, gillenwater-2014}.

Some corporate and industrial (\gls{ci}) buyers recognised the problems associated with the unbundled certificates and turned towards Power Purchase Agreements (\gls{ppa}s).
When signing a \gls{ppa}, energy buyers pledge to buy both the energy and the environmental credits \enquote{bundled} to megawatt-hours.
Market-driven procurement of renewable energy has become one of the major drivers of the energy transition: \gls{ppa}s are expected to account for one-fifth of utility solar PV and wind capacity expansion in 2023--2024, and almost twice as much (36\%) when China is excluded \cite{iea-REppa2023}.
In some countries, such as Spain and Sweden, market-driven procurement of renewable energy capacity surpasses policy-driven capacity expansion \cite{iea-REppa2023}.

\textbf{The key problem --} When \gls{ci} consumers purchase renewable credits, either via unbundled schemes or via bundled \gls{ppa}s, renewable energy supply is typically matched over a long period of time with buyers' energy demand.
As an example, more than 400 members of the RE100 group \cite{re100report-2020} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
Even the \enquote{best case} of 100\% annual matching commitments, where energy buyers sign \gls{ppa}s with renewable energy generators located within a local grid, has a major problem: the temporal mismatch between renewable energy supply and electricity demand.
In hours when wind and solar generation is low, energy buyers have to depend on carbon-emitting technologies, like coal and gas, available on local markets.
As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyer's portfolio.
Furthermore, the 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.

% 3. **24/7 Carbon-free Energy Procurement**
% Introduce the 24/7 CFE idea
% Initiatives corporate and NGO interest in 24/7 Carbon-free Energy Procurement

\textbf{One proposed solution: 24/7 CFE --} There is growing interest from the leaders in the clean energy procurement to move beyond the 100\% annual matching approach.
One approach is called 24/7 Carbon-Free Energy (\gls{cfe}) procurement, which aims to match clean energy supply with electricity demand on an \textit{hourly basis}.
Thus, 24/7~CFE procurement has the potential to eliminate all greenhouse gas emissions associated with electricity use of the participating companies.
Furthermore, 24/7~CFE procurement is focused on \textit{carbon-free} rather than renewable energy, which opens up opportunities for a broad range of advanced energy technologies, such as long-duration energy storage (\gls{ldes}) or new clean firm power generators that are needed for deep decarbonisation of energy systems.

Google initiated the 24/7 CFE movement in 2020 by announcing its commitment to cover the demand at all its data centres and campuses worldwide using the 24/7 CFE approach by 2030 \cite{google-247by2030}.
Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.	Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap} and methodologies paper for how to measure the progress \cite{google-methodologies}.
Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}.
The list of entities that have committed to 24/7 CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}. In 2021, an international group of energy suppliers, electricity buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact \cite{gocarbonfree247}.
With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, and solutions to make 24/7 Carbon-Free Energy achievable for all}.

% 5. **24/7 model-based studies review**

\textbf{Existing literature on 24/7 CFE --} The growing interest in the means, costs and the system-level impacts of hourly \gls{cfe} procurement has created a need for a quantitative analysis of the approach.
There is relatively little research on the system-level impacts of 24/7~CFE procurement; and it is all fairly recent.
The first to incorporate it into the electricity system planning model were Xu et al. (2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior report published in November 2021 investigating the system-level impacts of 24/7~CFE in two regions of the U.S. -- California and PJM \cite{xu-247CFE-report}.}
The authors study the system-level impacts of 24/7~CFE procurement based on an example of California in the year 2030.
In November 2022, IEA also released a model-based study on the 24/7~CFE, focusing on India and Indonesia \cite{ieaAdvancingDecarbonisationClean2022}.
In early 2023, Peninsula Clean Energy published an own white paper introducing their modeling tool---MATCH (Matching Around-the-Clock Hourly energy)---and the results of the modeling indicating feasibility of the company's \enquote{24/7 renewable energy by 2025} goal \cite{peninsula-report247}.

The first studies indicate that voluntary 24/7~CFE commitments reduce the emissions of participating buyers as well as emissions in the electricity grids they operate.
What has been missing is a comprehensive analysis of 24/7~CFE procurement over multiple regions and years, since electricity system characteristics, National Climate and Energy Plans (\gls{necp}s), renewable resource quality, and the cost of clean energy vary significantly across regions and over time.
Furthermore, it is unclear whether decarbonisation effect of 24/7 CFE procurement remains relevant when electricity grids are progressively decarbonised, as is the case in many countries and jurisdictions, or if the 24/7~CFE procurement is only impactful in the early stages of the energy transition.

% 6. **Relevance of this paper**

\textbf{Contribution --} The novelty of this study is to go beyond case studies and show in a systematic way, across many regions and levels of energy transition, how voluntary commitments to 24/7 CFE procurement impact participating buyers and regions where voluntary procurement occurs.
We explore different optimal procurement strategies for 24/7 CFE matching, costs associated with them, benefits for participating buyers, and impacts on system-level emissions.
Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.
Additionally, we examine the underlying mechanisms that drive the system-level reduction of CO$_2$ emissions, and examine how they perform over time and across regions.

% 7. **Prologue**

The remainder of the paper is structured as follows: \cref{sec:methods} introduces a mathematical model of clean energy procurement strategies and gives a brief summary of the methodology, sources of model input data, and the experimental setup.
The results are presented and discussed in \cref{sec:results} and put in perspective in \cref{sec:discussion}.
The work is concluded in \cref{sec:conclusion}.
\nameref{sec:si} provides further details about model assumptions and parametrisation of the background energy system.

\section{Methods and experimental design}
\label{sec:methods}

\textbf{Optimisation model --} The simulations were carried out with the modified version of the open European power system model PyPSA-Eur, built using the open framework PyPSA \cite{brownPyPSAPythonPower2018}.
The objective of the model is to minimise the annualised system-wide costs of meeting energy demand within the modelled system, while adhering to all relevant engineering, reliability, and policy constraints.
We use a brownfield investment approach, which means that we keep the existing power generation and storage assets in the model and only optimise the capacity expansion of new assets.
The optimal solution of the model includes the location and capacity of new power generation and storage assets, as well as the hourly dispatch of all existing and new assets, including the linear optimal power flow on the transmission network for the planning year.
This is standard for the PyPSA-Eur model \cite{horschPyPSAEurOpenOptimisation2018} and the long-term energy planning models of this class \cite{jenkinsGenX2022, howellsOSeMOSYSOpenSource2011}.
The mathematical formulation of the model is available in PyPSA documentation \cite{pypsadocs}.
The code to reproduce the optimisation problem behind this analysis is available at GitHub \cite{github-247CFEpaper}.

\textbf{Clean energy procurement model --} We introduce new model components (parameters, variables, constraints) into the PyPSA-Eur model to represent voluntary clean energy procurement.
By incorporating these into the mathematical problem, we model a situation where a fraction of electricity demand in a particular bidding zone is voluntarily committed to procuring clean energy with a desired strategy.
The fraction is set at 10\% of the total \gls{ci} electricity demand in a particular bidding zone, representing a hypotetical group of electricity consumers (e.g. datacentres, industrial facilities, or municipalities) committed to clean energy procurement, hereinafter referred to as \enquote{participating consumers}.
The model seeks to find cost-optimal procurement strategy and operational decisions for the participating consumers to meet their electricity demand in accordance with the chosen clean electricity matching strategy.

We model and compare two procurement strategies:

\begin{itemize}[-]
    \item \textit{100\% annual matching}: participating buyers meet their energy demand on an annual volumetric basis with additional renewable energy procurement;
    \item \textit{24/7 hourly matching}: participating buyers optimise their investment and operational decisions mixing procurement of additional generation and storage resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality score.
    \item For benchmarking, we also model \textit{a reference case}: participating buyers have no voluntary environmental commitments and purchase all their electricity from the local grid.
\end{itemize}

\textit{100\% annual matching --} The annual volumetric renewable matching strategy is modelled with a constraint (\ref{eqn:RES100}).
More formally, the sum of all dispatch $g_{r,t}$ of contracted renewable generators $r\in RES$ over the year $t\in T$ is equal to the annual electricity demand of participating consumers:
\begin{equation}
\sum_{r\in RES, t\in T} g_{r,t} = \sum_{t\in T} d_t
\label{eqn:RES100}
\end{equation}

The contracted renewable generators must be new, i.e., they must be additional to the system.
Procured generators can be sited only in the local bidding zone; thus, we model the \enquote{best case} of the annual matching strategy.

\textit{24/7 CFE hourly matching --} The hourly matching strategy is modelled with a constraint (\ref{eqn:CFE}). The 24/7~CFE procurement framework is based on the methodologies and metrics paper by Google~(2021) \cite{google-methodologies}. The framework considers various \gls{cfe} supply options for the participating consumers, including procurement of their own generation resources and storage assets, and electricity imports from the local grid.

More formally, the hourly generation from the procured CFE generators $r\in CFE$, discharge and charge from the procured storage technologies $s\in STO$, plus imports of electricity from the regional grid $im_t$ multiplied by the grid's hourly CFE factor $CFE_t$ minus the excess of the CFE supply must be higher or equal than a certain CFE score $x$ multiplied by the total load of participating consumers:

\begin{equation}
    \begin{split}
        \sum_{r\in CFE, t\in T} g_{r,t} &+ \sum_{s\in STO, t\in T} \left(\bar{g}_{s,t} - \underline{g}_{s,t}\right) \\
        &- \sum_{t\in T} ex_t + \sum_{t\in T} CFE_t \cdot im_t \geq x \cdot \sum_{t\in T} d_t
    \end{split}
\label{eqn:CFE}
\end{equation}

% On CFE target
\noindent where \textit{CFE score} $x$[\%] measures the degree to which hourly electricity consumption is matched with carbon-free electricity generation.
Equation (\ref{eqn:CFE}) thus allows for controlling \textit{the quality score} of the 24/7~CFE procurement by adjusting the parameter $x$. The best quality score---100\% CFE---means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.

% On locational matching and additionality
Similarly to the hourly matching strategy, the contracted generators must be additional to the system and can be sited only in the local bidding zone.

% On excess
Note that if total electricity generation of assets procured by participating consumers exceeds demand in a given hour, the \enquote{excess} carbon-free electricity is not counted toward a CFE score.
Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices.
We set a constraint on the total amount of excess generation sold to the regional grid, setting the limit to 20\% of the total annual demand of participating consumers.\footnote{In \nameref{sec:discussion}, we explain the rationale behind this limit and discuss the implications of this assumption.}
The wholesale market prices are derived from dual variables of a nodal energy balance constraint.

% On bilinear term due to grid CFE factor
The CFE factor of the regional grid ($CFE_t$) can be seen as the percentage of clean electricity in each MWh of imported electricity to supply demand of participating consumers in a given hour.
To compute $CFE_t$, we consider both the hourly electricity mix in the local bidding zone and emission intensity of imported electricity from the neighbouring zones.
The methodology to calculate the CFE factor of the grid is described in the prior work of the authors \cite{riepin-zenodo-systemlevel247}.

Note that in equation (\ref{eqn:CFE}), $CFE_t$ is affected by additional CFE resources procured by the participating consumers.
This introduces a nonconvex term to the optimisation problem.
The nonconvexity can be avoided by treating the grid CFE factor as a parameter that is iteratively updated (starting with $CFE_t =0 \,~\forall t$).
We find that one forward pass (i.e. 2 iterations) yields very good convergence.

\textbf{Model scope --} Geographically, the model encompasses the entire \gls{entsoe} area, which covers the entire European electricity system.\footnote{Islands that are not connected to the main European system, such as Malta, Crete and Cyprus, are excluded from the model.}
In this study, electricity demand, supply and power transmission infrastructure (alternating current lines at and above 220~kV voltage level and all high voltage direct current lines) are clustered to 37 individual bidding zones \cite{PyPSAEur-docs}.
Thus, each zone represents a country; some countries straddling different synchronous areas are split into individual bidding zones, such as DK1 (West) and DK2 (East).

Participating consumers can be located in either of the four selected zones: Ireland, Denmark (zone DK1), Germany, or Poland.
The comparison of results across these zones allows us to generalize the implications of voluntary clean energy procurement, taking into account individual characteristics of each zone, such as electricity demand, weather, availability of renewable resources, existing electricity generation capacity mix, and national energy policies, among other factors.

We model two individual years: 2025 and 2030.
From a modelling perspective, a five-year step changes many system parameters.
In particular, technology costs decline as a result of economies of scale and incremental innovation, \gls{necp}s become tighter, \co~prices increase, and some legacy power plants go out of business.
The problem is solved with a temporal resolution of 2920 snapshots, representing a 3-hourly average of the hourly time-series data.

\textbf{Carbon-free energy technologies in scope --} Depending on the scenario, participating consumers can choose from a variety of energy technologies available on the European market. By grouping technologies according to their maturity levels and availability on the market, we formulate three scenarios:

\begin{itemize}[-]
    \item \textit{Palette 1} -- technologies that are commercially available today: onshore wind, utility scale solar photovoltaics (\gls{PV}), and battery storage;
    \item \textit{Palette 2} -- all above plus a long-duration energy storage (\gls{ldes}) that is expected to be commercially available in the near future;
    \item \textit{Palette 3} -- all above plus promising advanced technologies that are in prototype stage today, but are expected to be commercially available in the future: (i) Allam cycle power plant with \gls{ccs}\footnote{Allam cycle is a natural gas power plant with up to 100\% of carbon capture and sequestration} to represent a technology option with higher operational expences (\gls{opex}), and (ii) \enquote{an advanced dispatchable generator}, a stand-in for clean firm technologies with higher capital expences (\gls{capex}), such as advanced geothermal or nuclear systems.
\end{itemize}

\textbf{Technology assumptions --} Cost and other assumptions for energy technologies available for participating consumers were collected primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in [\cref{tab:tech_costs}].
For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion.
Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, we use own indicative assumptions.

\textbf{Other assumptions --} Other model inputs and key background system assumptions are provided in [\labelcref{sec:si_2}]. For a full list of technology assumptions, see the GitHub repository \cite{github-247CFEpaper}.

\section{Results}
\label{sec:results}

Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
From the \gls{ci} buyers' perspective, we examine optimal procurement strategies for both annual and hourly matching strategies (i.e., a cost-optimal mix of locally procured energy generation, storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
From a system perspective, we analyze how voluntary clean energy procurement impacts CO$_2$ emissions in the background grid and the \enquote{demand pull} for advanced energy technologies.

Our experimental setup incorporates a wide range of scenarios, allowing us to generalise our results beyond individual assumptions.
For convenience, we start with a \textit{base scenario} presented in \cref{subsec:base}.
The base scenario reflects a case when 10\% (on volumetric basis) of \gls{ci} consumers in \textit{Ireland} in \textit{2025} are committed to procuring additional clean energy with a desired strategy.
The participating consumers can attain the 24/7~CFE procurement targets by co-optimizing local procurement using mature technologies, designated as \textit{palette~1}, and by importing electricity from the local grid.
Afterward, we delve deeper into the scenario space, altering selected parameters to explore various alternatives and address the following questions:

\begin{enumerate}[-]
\item \cref{subsec:palette}: What if a wider palette of carbon-free technologies were available to participating buyers?
\item \cref{subsec:location}: What if participating buyers are located in areas of the European electricity grid that differ significantly from the base scenario?
\item \cref{subsec:time}: What are the implications if we move the timeframe ahead five years to 2030?
\item Finally, in \cref{subsec:mechanisms}, we get a closer look at how 24/7 CFE commitments can help decarbonize local grids and reveal the individual mechanisms involved.
\end{enumerate}

Considering the large scenario space, this work presents results for a selection of scenario branches that generalise the system impacts of the 24/7 carbon-free energy procurement.
We publish all code to reproduce the experiments under open license alongside the paper.
See \nameref{sec:code}.

\subsection{Base scenario}
\label{subsec:base}

\begin{res}
    Through 24/7 CFE procurement, participating consumers can eliminate carbon emissions associated with their electricity consumption and help to decarbonise the entire electricity system.
\end{res}

\begin{res}
    90\%--95\% 24/7 CFE targets have only a small cost premium over 100\% annual renewable matching. 100\%~CFE target can be achieved with solar PV, wind and battery storage, but at a high cost premium for participating consumers.
\end{res}

%some parts of this paragraph may go to methods
\cref{fig:10-2025-IE-p1-used} shows the fraction of hourly demand met with \gls{cfe} depending on the procurement policy that participating consumers follow.
We contrast two main cases, one where participants commit to 100\% annual renewable matching policy (hereinafter -- \enquote{100\% RES}) and another case where the consumers commit to 24/7~CFE hourly matching policy (hereinafter -- \enquote{24/7~CFE}) with various CFE targets in a range from 80\% to 100\%.
In the \textit{reference case}, participating consumers cover their load purely with grid purchases without any policy regarding the origin of electricity.

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-used.pdf}
    \caption{Fraction of hourly demand met with carbon-free electricity.}
    \label{fig:10-2025-IE-p1-used}
\end{figure}

In the reference case, only 54\% of demand is met with \gls{cfe}.
100\% RES---the best case for the annual renewable matching policy---results in a 83\% fraction.
Consequently, CFE targets beyond 85\% yield higher share of hourly demand met with \gls{cfe} than 100\%~RES.
Another notable trend in \cref{fig:10-2025-IE-p1-used} is that participating consumers rely more on procured resources and less on grid imports with higher CFE targets.
When targets approach 100\%, participating consumers cannot rely on electricity imports from the grid, since the grid supply mix contains some carbon content in almost all hours.

\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of participating consumers.
The average emissions rate is derived by dividing the total CO$_2$ emissions linked to the electricity consumption of participating consumers by the total kilowatt-hours (kWh) consumed.
Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case.
If participating consumers follow 100\%~RES policy, the emission rate is reduced to 60~g\co/kWh.
This yields a considerable emission rate reduction compared to the reference case.
The 24/7~CFE procurement with targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\%~RES.
At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and \gls{cfe} supply on an hourly basis.

Voluntary procurement of clean electricity also helps decarbonise the electricity system as a whole.
We explore this effect by plotting CO$_2$ emissions in the local region of the participating consumers, i.e. Ireland (\cref{fig:10-2025-IE-p1-zone_emissions}).
Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2 Mt\co/a.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~MtCO$_2$ in 2021. A strong decreasing trend is expected, since the Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~Mt\co/a, in contrast to a scenario absent voluntary procurement.
This reduction equates to 14\% of the total emissions from the Irish power sector.
100\%~RES can also facilitate system-level CO$_2$ emissions reductions (as depicted by the left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, 24/7~CFE attains superior emissions reductions when the CFE target surpasses 85\%.

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Average emissions rate of participating consumers.}
        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_emisrate.pdf}
        \label{fig:10-2025-IE-p1-ci_emisrate}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{CO$_2$ emissions in the local region (Ireland).}
        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-zone_emissions.pdf}
        \label{fig:10-2025-IE-p1-zone_emissions}
    \end{subfigure}
    \caption{Impact of clean electricity procurement commitments on emissions of participating consumers (top panel) and the system-level emissions in a local region (bottom panel).}
    \label{fig:10-2025-IE-p1-emissions}
\end{figure}

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \caption{Portfolio capacity procured by participating consumers.}
        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_capacity.pdf}
        \label{fig:10-2025-IE-p1-ci_capacity}
    \end{subfigure}
    \begin{subfigure}[t]{0.95\columnwidth}
        \centering
        \vspace{-0.2cm}
        \caption{Cost breakdown of a procurement policy.}
        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_costandrev.pdf}
        \label{fig:10-2025-IE-p1-ci_costandrev}
    \end{subfigure}
    \caption{Optimal capacity portfolios (top panel) and costs breakdown (bottom panel) per procurement strategy.}
    \label{fig:10-2025-IE-p1-ci_procurement}
\end{figure}

The following analysis unveils the modelled cost-optimal procurement strategies for each procurement policy (\cref{fig:10-2025-IE-p1-ci_capacity}).
In Ireland, 10\% of the \gls{ci} sector's demand yields a load of 220~MW.
The findings indicate that, to cover this load adhering to a 100\%~RES policy, participating consumers procure a combined capacity of 1.3~GW from onshore wind and solar PV generators.
Ensuring demand is matched with \gls{cfe} on an hourly basis requires a considerably more substantial portfolio of wind and solar PV, up to 4.0~GW of combined capacity to reach the 100\%~CFE target.
Batteries are integrated into the cost-optimal portfolio mix when CFE targets exceed 85\%.
It is noteworthy that, for an 80\%~CFE target, participating consumers procure less capacity than under a 100\%~RES policy, as they rely more on grid imports.

The breakdown of costs associated with a procurement policy that participating consumers choose is shown in \cref{fig:10-2025-IE-p1-ci_costandrev}.
Note that revenues from selling the excess electricity to the regional grid at market prices can be treated as \enquote{negative costs} and subtracted from the net procurement cost.
The results show that a CFE targets of 80\%--95\% can be achieved at a small cost premium to 100\%~RES policy with solar, wind and batteries.
However, what stands out in the plot is the rapid increase of procurement costs for high 24/7 CFE targets.
For example, 98\% CFE target has cost premium of 54\% over 100\% the annual matching policy; while the last 2\% of hourly matching more than doubles the costs.

\subsection{Technology access}
\label{subsec:palette}

\begin{res}
    24/7 CFE procurement creates an early market for advanced energy technologies the system will need later: long-duration energy storage and clean firm generators.
\end{res}

>>>>

% format hacks
\usepackage{libertine}
\usepackage{libertinust1math}
\usepackage{amsmath}                 % Provides advanced math typesetting and environments
\usepackage{bbold}                   % Provides blackboard bold font for numbers
\usepackage{graphicx}                % Handles the inclusion of graphics files
\usepackage{eurosym}                 % Provides the Euro currency symbol
\usepackage{mathtools}               % Enhances amsmath package, adding new symbols and tools
\usepackage{url}                     % Handles the formatting of URLs
\usepackage{booktabs}                % Improves the quality of tables in LaTeX
\usepackage{epstopdf}                % Automatically converts EPS files to PDF
\usepackage{xfrac}                   % Provides a consistent way to typeset fractions
\usepackage{tabularx}                % Enhances the standard LaTeX tables
\usepackage{bm}                      % Provides access to bold math symbols
\usepackage{subcaption}              % Provides support for subfigures and subtables
\usepackage{longtable}               % Allows the creation of multi-page tables
\usepackage{multirow}                % Enables cells spanning multiple rows in tables
\usepackage{threeparttable}          % Provides additional functionality for tables
\usepackage{pdflscape}               % Allows landscape pages in PDF output
\usepackage[svgnames]{xcolor}    	 % Load xcolor packages
\usepackage[export]{adjustbox}       % Provides tools for resizing and trimming images
\usepackage[version=4]{mhchem}       % Provides typesetting for chemical equations
\usepackage{xurl} 				     % Allows line breaks in URLs
\usepackage[colorlinks]{hyperref}    % Creates hyperlinks in the document
\usepackage[parfill]{parskip}        % Adjusts paragraph spacing
\usepackage[nameinlink,sort&compress,capitalise,noabbrev]{cleveref} % Enhanced cross-referencing
\usepackage[leftcaption,raggedright]{sidecap} % Provides side captions for figures and tables
\usepackage[prependcaption,textsize=footnotesize]{todonotes} % Allows inline and margin notes
\usepackage{siunitx}                 % Provides consistent formatting for units and numbers
\usepackage{csquotes} 				 % For handling inline and display quotations

@@

@@
